Technique for \earlywarning\ detection of compact binary coalescence and its implication for multimessenger astronomy

### 2011-06-01 analysis.tex
label and typos
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@810 ccdd05d5-56c1-461a-bf98-85f6876523b4

\section{Implementation}

@@

\subsubsection{\SNR accumulation}

In order to accumulate \SNR\ for an early warning, the time slice filter
output is upsampled to the next highest frequency time slice and summed. This
process is iterated until the final \SNR is computed.  However at each stage
of upsampling the summed filter outputs are related to the early warning \SNR
by a simple normalization factor that can be computed in advance. Thus the
\lloid\ algorithm and this implementation leads to a simple early warning
pipeline with little additional work.

>>>>

\section{Implementation}
\label{sec:implementation}

@@

\subsubsection{\SNR\ accumulation}

In order to accumulate \SNR\ for an early warning, the time slice filter
output is upsampled to the next highest frequency time slice and summed. This
process is iterated until the final \SNR\ is computed.  However at each stage
of upsampling the summed filter outputs are related to the early warning \SNR\
by a simple normalization factor that can be computed in advance. Thus the
\lloid\ algorithm and this implementation leads to a simple early warning
pipeline with little additional work.
